### 2025-01-30 paper/preprint/paper.tex
vamos
progress on appendix

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{exercise}{Parameters}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\section{Appendix}\label{appendix}

\subsection{Training Details}\label{training-details}

@@

The hyperparameter choices are shown in
Parameters~\ref{exr-gen-params-first-run}:

\begin{exercise}[Parameters]\protect\hypertarget{exr-gen-params-first-run}{}\label{exr-gen-params-first-run}

@@

\begin{itemize}
\tightlist
\item
  \textbf{generator\_params}:

  \begin{itemize}
  \tightlist
  \item
    \textbf{lambda\_cost}: 0.0, 0.001, 0.1
  \item
    \textbf{lambda\_energy}: 0.01, 0.05, 0.1, 0.5, 1.0, 5.0, 10.0, 15.0
  \item
    \textbf{lr}: 1.0
  \item
    \textbf{maxiter}: 20, 50, 100
  \item
    \textbf{opt}: sgd
  \end{itemize}
\item
  \textbf{generator\_type}: ecco, generic, omni, revise
\item
  \textbf{training\_params}:

  \begin{itemize}
  \tightlist
  \item
    \textbf{objective}: full, vanilla
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Energy Penalty} (Table~\ref{tbl-lin_sep-lambda_energy_exper}):
  \emph{ECCo} generally does yield better results than \emph{Vanilla}
  for higher choices of the energy penalty (10,15) during training.
  \emph{Generic} performs poorly accross the board. \emph{Omni} seems to
  have an anchoring effect, in that it never performs terribly but also
  never as good as the best \emph{ECCo} results. \emph{REVISE} performs
  poorly across the board.
\item
  \textbf{Cost (distance penalty)}: Results for all generators (except
  \emph{Omni}) are quite bad, which can likely be attributed to
  extremely bad results for some choices of the \textbf{Energy Penalty}
  (results here are averaged). For \emph{ECCo} and \emph{Generic},
  higher cost values generally lead to worse results.
\item
  \textbf{Maximum Iterations}: No clear patterns recognizable, so it
  seems that smaller choices are ok.
\item
  \textbf{Validity}: \emph{ECCo} almost always valid except for very low
  values during training and high values at evaluation time.
  \emph{Generic} often has poor validity.
\item
  \textbf{Accuracy}: Seems largely unaffected.
\end{itemize}

@@

>>>>

\usepackage{arxiv}
\usepackage{orcidlink}
\usepackage{amsmath}
\usepackage[T1]{fontenc}
\usepackage{placeins}
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\usepackage{amsthm}
\theoremstyle{definition}
\newtheorem{exercise}{Parameters}[section]
\theoremstyle{remark}
\AtBeginDocument{\renewcommand*{\proofname}{Proof}}
\newtheorem*{remark}{Remark}
\newtheorem*{solution}{Solution}
\newtheorem{refremark}{Remark}[section]
\newtheorem{refsolution}{Solution}[section]
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

@@

\newpage{}

\FloatBarrier

\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

\setcounter{figure}{0}
\renewcommand{\thefigure}{A\arabic{figure}}

\section{Training Details}\label{training-details}

@@

The hyperparameter grids for the first investigation of the effect of
generator parameters are shown in
Parameters~\ref{exr-gen-params-first-run-train} and
Parameters~\ref{exr-gen-params-first-run-eval}.

\begin{exercise}[Training
Phase]\protect\hypertarget{exr-gen-params-first-run-train}{}\label{exr-gen-params-first-run-train}

@@

\begin{itemize}
\tightlist
\item
  Generator Parameters:

  \begin{itemize}
  \tightlist
  \item
    \(\lambda_{\text{cost}}\): \texttt{0.0,\ 0.001,\ 0.1}
  \item
    \(\lambda_{\text{div}}\):
    \texttt{0.01,\ 0.05,\ 0.1,\ 0.5,\ 1.0,\ 5.0,\ 10.0,\ 15.0}
  \item
    Learning Rate: \texttt{1.0}
  \item
    Maximum Iterations: \texttt{20,\ 50,\ 100}
  \item
    Optimizerimizer: \texttt{sgd}
  \end{itemize}
\item
  Generator: \texttt{ecco,\ generic,\ omni,\ revise}
\item
  Training Parameters:

  \begin{itemize}
  \tightlist
  \item
    Objective: \texttt{full,\ vanilla}
  \end{itemize}
\end{itemize}

\begin{exercise}[Evaluation
Phase]\protect\hypertarget{exr-gen-params-first-run-eval}{}\label{exr-gen-params-first-run-eval}

\begin{itemize}
\tightlist
\item
  Counterfactual Parameters:

  \begin{itemize}
  \tightlist
  \item
    Convergence: \texttt{max\_iter}
  \item
    Maximum Iterations: \texttt{100}
  \item
    No.~Individuals: \texttt{100}
  \item
    No.~Runs: \texttt{5}
  \end{itemize}
\item
  Generator Parameters:

  \begin{itemize}
  \tightlist
  \item
    \(\lambda_{\text{cost}}\): \texttt{0.0}
  \item
    \(\lambda_{\text{div}}\):
    \texttt{0.1,\ 0.5,\ 1.0,\ 5.0,\ 10.0,\ 20.0}
  \item
    Learning Rate: \texttt{1.0}
  \item
    Maximum Iterations: \texttt{50}
  \item
    Optimizerimizer: \texttt{sgd}
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
\tightlist
\item
  \textbf{Energy Penalty} (Table~\ref{tbl-lin_sep-lambda_energy_exper}):
  \emph{ECCo} generally does yield better results than \emph{Vanilla}
  for higher choices of the energy penalty (10,15) during training.
  \emph{Generic} performs poorly accross the board. \emph{Omni} seems to
  have an anchoring effect, in that it never performs terribly but also
  never as good as the best \emph{ECCo} results. \emph{REVISE} performs
  poorly across the board.
\item
  \textbf{Cost} (Table~\ref{tbl-lin_sep-lambda_cost_exper}): Results for
  all generators (except \emph{Omni}) are quite bad, which can likely be
  attributed to extremely bad results for some choices of the
  \textbf{Energy Penalty} (results here are averaged). For \emph{ECCo}
  and \emph{Generic}, higher cost values generally lead to worse
  results.
\item
  \textbf{Maximum Iterations}: No clear patterns recognizable, so it
  seems that smaller choices are ok.
\item
  \textbf{Validity}: \emph{ECCo} almost always valid except for very low
  values during training and high values at evaluation time.
  \emph{Generic} often has poor validity.
\item
  \textbf{Accuracy}: Seems largely unaffected.
\end{itemize}

@@

\caption{\label{tbl-lin_sep-lambda_cost_exper}Results for Linearly
Separable data by cost penalty.}

  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{cost}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endfirsthead
  \toprule
  \textbf{Objective} & \textbf{$\lambda_{\text{cost}} (\text{train})$} & \textbf{Generator} & \textbf{Value} & \textbf{Std} \\\midrule
  \endhead
  \bottomrule
  \multicolumn{5}{r}{Continuing table below.}\\
  \bottomrule
  \endfoot
  \endlastfoot
  full & 0 & \textit{ECCo} & $-5.32 \cdot 10^{3}$ & $1.21 \cdot 10^{4}$ \\
  full & 0 & \textit{Generic} & $-1.03 \cdot 10^{18}$ & $2.34 \cdot 10^{18}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.64}} & \color{blue}{\textbf{0.125}} \\
  full & 0 & \textit{REVISE} & -15.4 & 12.9 \\
  vanilla & 0 & \textit{ECCo} & -4.34 & 3.58 \\
  vanilla & 0 & \textit{Generic} & -4.41 & 3.48 \\
  vanilla & 0 & \textit{Omniscient} & -5.18 & 4.54 \\
  vanilla & 0 & \textit{REVISE} & -4.93 & 4.23 \\
  full & 0.001 & \textit{ECCo} & -362 & 811 \\
  full & 0.001 & \textit{Generic} & $-2.65 \cdot 10^{17}$ & $6.03 \cdot 10^{17}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.001}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.49}} & \color{blue}{\textbf{0.115}} \\
  full & 0.001 & \textit{REVISE} & -15.5 & 13 \\
  vanilla & 0.001 & \textit{ECCo} & -4.34 & 3.58 \\
  vanilla & 0.001 & \textit{Generic} & -4.41 & 3.48 \\
  vanilla & 0.001 & \textit{Omniscient} & -5.18 & 4.53 \\
  vanilla & 0.001 & \textit{REVISE} & -4.93 & 4.23 \\
  full & 0.1 & \textit{ECCo} & $-3.72 \cdot 10^{11}$ & $8.46 \cdot 10^{11}$ \\
  full & 0.1 & \textit{Generic} & $-4.49 \cdot 10^{14}$ & $1.02 \cdot 10^{15}$ \\
  \color{blue}{\textbf{full}} & \color{blue}{\textbf{0.1}} & \color{blue}{\textbf{Omniscient}} & \color{blue}{\textbf{-2.5}} & \color{blue}{\textbf{0.112}} \\
  full & 0.1 & \textit{REVISE} & -14.6 & 12.2 \\
  vanilla & 0.1 & \textit{ECCo} & -4.34 & 3.58 \\
  vanilla & 0.1 & \textit{Generic} & -4.41 & 3.48 \\
  vanilla & 0.1 & \textit{Omniscient} & -5.18 & 4.54 \\
  vanilla & 0.1 & \textit{REVISE} & -4.93 & 4.24 \\\bottomrule

### 2025-01-30 paper/sections/appendix.qmd
vamos
progress on appendix

# Appendix

## Training Details

@@

The hyperparameter choices are shown in @exr-gen-params-first-run:

::: {#exr-gen-params-first-run}

## Parameters

@@

@@

- **Energy Penalty** (@tbl-lin_sep-lambda_energy_exper): *ECCo* generally does yield better results than *Vanilla* for higher choices of the energy penalty (10,15) during training. *Generic* performs poorly accross the board. *Omni* seems to have an anchoring effect, in that it never performs terribly but also never as good as the best *ECCo* results. *REVISE* performs poorly across the board.
- **Cost (distance penalty)**: Results for all generators (except *Omni*) are quite bad, which can likely be attributed to extremely bad results for some choices of the **Energy Penalty** (results here are averaged). For *ECCo* and *Generic*, higher cost values generally lead to worse results.
- **Maximum Iterations**: No clear patterns recognizable, so it seems that smaller choices are ok. 
- **Validity**: *ECCo* almost always valid except for very low values during training and high values at evaluation time. *Generic* often has poor validity.
- **Accuracy**: Seems largely unaffected.

@@

>>>>

\FloatBarrier

\setcounter{section}{0}
\renewcommand{\thesection}{\Alph{section}}

\setcounter{table}{0}
\renewcommand{\thetable}{A\arabic{table}}

\setcounter{figure}{0}
\renewcommand{\thefigure}{A\arabic{figure}}

<!-- # Supplementary Material {.appendix} -->

# Training Details {.appendix}

@@

The hyperparameter grids for the first investigation of the effect of generator parameters are shown in @exr-gen-params-first-run-train and @exr-gen-params-first-run-eval.

::: {#exr-gen-params-first-run-train}

## Training Phase

@@

::: {#exr-gen-params-first-run-eval}

## Evaluation Phase

```{julia}
#| output: asis
dict = CTExperiments.from_toml(joinpath(results_dir, "gen_params/mlp/lin_sep/evaluation/evaluation_grid_config.toml"))
println(CTExperiments.dict_to_quarto_markdown(dict))
```

@@

- **Energy Penalty** (@tbl-lin_sep-lambda_energy_exper): *ECCo* generally does yield better results than *Vanilla* for higher choices of the energy penalty (10,15) during training. *Generic* performs poorly accross the board. *Omni* seems to have an anchoring effect, in that it never performs terribly but also never as good as the best *ECCo* results. *REVISE* performs poorly across the board.
- **Cost** (@tbl-lin_sep-lambda_cost_exper): Results for all generators (except *Omni*) are quite bad, which can likely be attributed to extremely bad results for some choices of the **Energy Penalty** (results here are averaged). For *ECCo* and *Generic*, higher cost values generally lead to worse results.
- **Maximum Iterations**: No clear patterns recognizable, so it seems that smaller choices are ok. 
- **Validity**: *ECCo* almost always valid except for very low values during training and high values at evaluation time. *Generic* often has poor validity.
- **Accuracy**: Seems largely unaffected.

@@

<!-- Cost -->

```{julia}
df = CSV.read("$(gen_params_dir)/lin_sep/evaluation/results/ce/objective---lambda_cost_exper---lambda_energy_eval/plausibility_distance_from_target.csv", DataFrame)
df = groupby(df, Not(:run, :std, :mean, :lambda_energy_eval)) |> 
  gdf -> combine(gdf, :mean => (x -> [(mean(x),std(x))]) => [:value,:std]) |>
  df -> sort(df, [:lambda_cost_exper, :objective, :generator_type])
```

::: {#tbl-lin_sep-lambda_cost_exper}

```{julia}
#| output: asis
get_table_inputs(df, "value"; alpha=0.9, byvars="lambda_cost_exper", backend=Val(:latex)) |>
    inputs -> tabulate_results(inputs; wrap_table=false)
```

Results for Linearly Separable data by cost penalty.
